Supplemental Materials: \emph{Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours}

### 2015-03-20 Publications/2015-NeuroImage/00-main.tex
update figure, updates in manuscript
final fixes
update supplementals
editions after @daducci review

\title{Active-contours driven registration of diffusion MR images of the brain}

\author[bit]{Oscar~Esteban\corref{corrauthor}}
\cortext[corrauthor]{Corresponding author}
\ead{phd@oscaresteban.es}
\author[ucla]{Dominique~Zosso}
\author[lts5]{Alessandro~Daducci}
\author[chuv,lts5]{Meritxell~Bach-Cuadra}
\author[bit]{Mar\'ia-J.~Ledesma-Carbayo}
\author[lts5]{Jean-Philippe~Thiran}
\author[bit]{Andr\'es~Santos}

\address[bit]{Biomedical Image Technologies (BIT), ETSI Telecomunicaci\'on, %
Universidad Polit\'ecnica de Madrid and CIBER-BBN, Madrid, Spain}
\address[ucla]{Department of Mathematics, University of California,
Los Angeles (UCLA), Los Angeles, CA, US}
\address[lts5]{Signal Processing Laboratory (LTS5), \'Ecole Polytechnique
F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
\address[chuv]{Dept. of Radiology, University
Hospital Center (CHUV) and University of Lausanne (UNIL), Lausanne, Switzerland}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{keyword}
diffusion MRI \sep susceptibility~distortion \sep segmentation %
\sep registration \sep parcellation \sep shape-prior.
\end{keyword}

@@

%\bibliographystyle{plainnat}
\bibliographystyle{mystyle}
\bibliography{Remote}

>>>>

\title{Active-contours driven registration applied in the correction of
susceptibility-derived distortions of diffusion MR images}

\author[bit]{Oscar~Esteban\corref{corrauthor}}
\cortext[corrauthor]{Corresponding author}
\ead{phd@oscaresteban.es}
\author[ucla]{Dominique~Zosso}
\author[scil,lts5]{Alessandro~Daducci}
\author[chuv,lts5]{Meritxell~Bach-Cuadra}
\author[bit]{Mar\'ia-J.~Ledesma-Carbayo}
\author[lts5]{Jean-Philippe~Thiran}
\author[bit]{Andr\'es~Santos}

\address[bit]{Biomedical Image Technologies (BIT), ETSI Telecomunicaci\'on, %
Universidad Polit\'ecnica de Madrid and CIBER-BBN, Madrid, Spain}
\address[ucla]{Department of Mathematics, University of California,
Los Angeles (UCLA), Los Angeles, CA, US}
\address[scil]{Computer Science Department, Faculty of Science, Universit\'e de Sherbrooke, 2500 Boulevard Universit\'e, Sherbrooke, QC J1K 2R1, Canada}
\address[lts5]{Signal Processing Laboratory (LTS5), \'Ecole Polytechnique
F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
\address[chuv]{Dept. of Radiology, University
Hospital Center (CHUV) and University of Lausanne (UNIL), Lausanne, Switzerland}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{keyword}
diffusion MRI \sep susceptibility~distortion \sep segmentation %
\sep nonlinear~registration \sep active~contours \sep echo-planar imaging.
\end{keyword}

@@

%\bibliographystyle{plainnat}
% \section*{References}
\bibliographystyle{mystyle}
\bibliography{Remote}

### 2015-03-20 Publications/2015-NeuroImage/02-abstract.tex
introducing final results
editions after @daducci review

% -*- root: 00-main.tex -*-
We propose a simultaneous segmentation and registration method called \emph{regseg}
  that uses active contours without edges extracted from structural images.
The contours evolve through a free-deformation field of B-Spline functions that
  optimally maps the surfaces onto the data in the target space.
\emph{Regseg} is intended, but not limited, to correct susceptibility-derived distortions
  in echo-planar imaging.
We proof the concept behind \emph{regseg} on four digital phantoms warped with random
  deformations, and conclude that the precision of the segmentation is subvoxel.
Finally, we demonstrate \emph{regseg} in the correction task on 16 real diffusion MRI
  datasets from the \acrlong*{hcp}.
The results suggest that \emph{regseg} overperformed an extended competing method.
\emph{Regseg} showed a consistent error within the 95\% confidence interval of
  $0.39-0.93mm$ in images of $1.25mm$ isotropic resolution.

>>>>

% -*- root: 00-main.tex -*-
We propose a simultaneous segmentation and registration method called \emph{regseg}
  that uses active contours without edges extracted from structural images.
The contours evolve through a free-deformation field of B-Spline functions that
  optimally maps the surfaces onto the data in the target space.
\emph{Regseg} is intended, but not limited, to correct susceptibility-derived distortions
  in echo-planar imaging.
We proof the concept behind \emph{regseg} on four digital phantoms warped with random
  deformations, and conclude that the precision of the segmentation is subvoxel.
Finally, we demonstrate \emph{regseg} in the correction task on 16 real diffusion MRI
  datasets from the \acrlong*{hcp}.
The results suggest that \emph{regseg} overperformed an extended competing method.
We compute the geometrical disagreement of the surfaces registered with \emph{regseg} with
  respect to a ground truth, obtaining a 95\% confidence interval of $[1.08 - 1.50]mm$ in images 
  of $1.25mm$ isotropic resolution.
